---
title: "teacher_2d"
output: html_document
date: "2022-08-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(brms)
library(ggthemes)
library(tidyboot)

options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

theme_set(theme_few(base_size = 15))
```

```{r}
d.raw <- read.csv(here('data/teacher_2d/pilot1/expt3_data.csv'))

cat("Total participants: ", length(unique(d.raw$subject_id)), "\n")

d <- d.raw %>% 
  mutate(sequential = ifelse(block_type == "nonSeqFull" | block_type == "nonSeqPartial", "non_sequential", "sequential"),
        feedback = ifelse(block_type == "seqFeedback", "feedback", "no_feedback"),
        teacher_knowledge = ifelse(block_type == "nonSeqFull", "full", "partial"),
        trial_num = ifelse(trial_num == 0, 'lesson1', 'lesson2'), 
        student_idx = factor(student_idx), 
        stem_concept_size = ifelse(trueStemDir == 'greater', 8.5 - trueStemThresh, trueStemThresh - 0.5),
        cap_concept_size = ifelse(trueCapDir == 'greater', 8.5 - trueCapThresh, trueCapThresh - 0.5),
        stemDistFromBoundary = abs(stemResponse - trueStemThresh),
        capDistFromBoundary = abs(capResponse - trueCapThresh), 
        stemDistFromBoundary_norm = abs(stemResponse - trueStemThresh) / stem_concept_size,
        capDistFromBoundary_norm = abs(capResponse - trueCapThresh) / cap_concept_size, 
        corner = ifelse((abs(stemResponse - trueStemThresh) == 0.5) & (abs(capResponse - trueCapThresh) == 0.5), TRUE, FALSE), 
        known_concept_size = ifelse(prior == "stem", stem_concept_size, cap_concept_size), 
        unknown_concept_size = ifelse(prior == "stem", cap_concept_size, stem_concept_size), 
        dist_from_known = ifelse(prior == "stem", stemDistFromBoundary, capDistFromBoundary), 
        dist_from_unknown = ifelse(prior == "stem", capDistFromBoundary, stemDistFromBoundary)) %>%  
  select(-c(block_type, pass_attention)) %>% 
  filter(understood == "yes", n_attention_passed == 3)

cat("Total participants after exclusions: ", length(unique(d$subject_id)))
```

Make separate dataframe for sequential trials
```{r}
d.seq <- d %>%
  filter(sequential == 'sequential') %>% 
  pivot_wider(names_from = trial_num,
              values_from = c("corner", "dist_from_known", "dist_from_unknown"),
              id_cols = c("subject_id", 
                          "student_idx",
                          "prior", 
                          "feedback"))
```

# Non-sequential conditions

## Sanity checks 

Do people give examples that are a different distance from the boundary based on how big the concept space is? 
```{r}

```



In the full knowledge case, do participants consider what students know or don't know? 

```{r}
d.nonseq <- d %>% 
  filter(sequential == 'non_sequential') %>% 
  pivot_longer(
    cols = starts_with("dist_from"), 
    names_to = "known", 
    names_prefix = "dist_from_", 
    values_to = "dist"
  ) %>% 
  mutate(
    concept_size = ifelse(known == "known", known_concept_size, unknown_concept_size)
  ) %>% 
  select(subject_id, student_idx, concept_size, known_concept_size, unknown_concept_size, teacher_knowledge, corner, known, dist)
```

```{r}
nonseq.mod <- d.nonseq %>% lmer(
  dist ~ 1 + teacher_knowledge * known + (1 + teacher_knowledge * known | subject_id) + (1 + teacher_knowledge * known | concept_size), 
  data = .
)

summary(nonseq.mod)
```




```{r}
d.nonseq.corners <- d.nonseq %>% 
  group_by(teacher_knowledge, concept_size, known) %>% 
  tidyboot_mean(
    corner, na.rm = T
  )

d.nonseq.distances <- d.nonseq %>% 
  group_by(teacher_knowledge, concept_size, known) %>% 
  tidyboot_mean(
    dist, na.rm = T
  )

d.nonseq.corners
d.nonseq.distances
```
```{r}
ggplot(d.nonseq.distances, aes(x = teacher_knowledge, y = empirical_stat, color = known)) + 
    geom_point(size = 2, position = position_dodge(width = 0.1)) + 
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), size = 1, width = 0, position = position_dodge(width = 0.15)) + 
    theme(aspect.ratio = 1.2) + 
    scale_color_discrete(labels = c("known boundary", "unknown boundary")) +
    labs(x = "teacher knowledge", y = "distance to boundary", title = "different 1d concept sizes", col = "student knowledge") +
     facet_wrap(~concept_size)
```
Look at corners

```{r}
ggplot(d.nonseq.corners, aes(x = teacher_knowledge, y = empirical_stat, color = known)) + 
    geom_point(size = 2, position = position_dodge(width = 0.1)) + 
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), size = 1, width = 0, position = position_dodge(width = 0.15)) + 
    theme(aspect.ratio = 1.2) + 
    scale_color_discrete(labels = c("known boundary", "unknown boundary")) +
    labs(x = "teacher knowledge", y = "proportion corners", title = "proportion corners", col = "student knowledge") +
     facet_wrap(~concept_size)

```


What if we break it out by true hypothesis? 

```{r}
d.nonseq.corners <- d.nonseq %>% 
  group_by(teacher_knowledge, known_concept_size, unknown_concept_size, known) %>% 
  tidyboot_mean(
    corner, na.rm = T
  )

d.nonseq.distances <- d.nonseq %>% 
  group_by(teacher_knowledge, known_concept_size, unknown_concept_size, known) %>% 
  tidyboot_mean(
    dist, na.rm = T
  )

```

```{r}
known_concept_size.labs <- c("known: 2", "known: 4", "known: 6")
names(known_concept_size.labs) <- c(2, 4, 6)

unknown_concept_size.labs <- c("unknown: 2", "unknown: 4", "unknown: 6")
names(unknown_concept_size.labs) <- c(2, 4, 6)

ggplot(d.nonseq.distances, aes(x = teacher_knowledge, y = empirical_stat, color = known)) + 
    geom_point(size = 1.5, position = position_dodge(width = 0.15)) + 
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), size = 1, width = 0, position = position_dodge(width = 0.15)) + 
    theme(aspect.ratio = 1) + 
    scale_color_discrete(labels = c("known boundary", "unknown boundary")) +
    labs(x = "teacher knowledge", y = "distance to boundary", title = "distance to boundary for each concept dimension", col = "student knowledge") +
     facet_grid(known_concept_size ~ unknown_concept_size, labeller = labeller(known_concept_size = known_concept_size.labs, unknown_concept_size = unknown_concept_size.labs)) + 
  theme_few(base_size = 14)
```


# What about the sequential conditions? 


