---
title: "Random effects by teacher/problem"
author: "Natalia Vélez"
date: "7/26/2022"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Setup:
```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(sjPlot)
library(arm)
library(ggthemes)
```

## Run regression
Load student data:
```{r}
student_df = read.csv('outputs/student_beliefs.csv') %>%
  # mutate_at(c('worker', 'teacher', 'problem'), factor) %>% # categorical vars
  rename(student = worker)

print(head(student_df))
str(student_df)
```

# Run regression
```{r}
student_reg = lmer(belief_in_true ~ num_hint*teacher_rating + (1|problem) +
                     (1|student) + (1|teacher), data=student_df)
print(summary(student_reg))
```
# Random effects

### Teacher

Get random effects and SE:
```{r}
teacher_eff = ranef(student_reg) %>%
  .$teacher %>%
  rename('random_intercept' = '(Intercept)') %>%
  mutate(subject = as.numeric(rownames(.)),
         se = se.ranef(student_reg)$teacher)
```

Plot teacher random effects:
```{r}
ggplot(teacher_eff, aes(x = reorder(subject, -random_intercept), y = random_intercept)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin=random_intercept-se, ymax=random_intercept+se), width=0) +
  theme_few(base_size=18) +
  xlab('Teachers (reordered)') +
  ylab('Random intercepts') +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())
# ggsave('plots/teacher_ranef.pdf', width=6.73, height=6.73/2)
```

Check: How much did people make for the worst and best teachers?
```{r}
performance_by_teacher = student_df %>%
  group_by(student, teacher, problem) %>%
  summarise(bonus = sum(bonus)) %>%
  group_by(teacher) %>%
  summarise(avg_bonus = mean(bonus),
            sd_bonus = sd(bonus)) %>%
  rename(subject = teacher) %>%
  left_join(teacher_eff) %>%
  arrange(-random_intercept) %>%
  ungroup()

print('Best teacher:')
print(head((performance_by_teacher)))

print('Worst teacher:')
print(tail((performance_by_teacher)))
```
Check: Are random intercepts correlated with average performance (as indexed by the amount of bonus awarded)?
```{r}
ggplot(performance_by_teacher, aes(x=avg_bonus, y=random_intercept)) +
  geom_point() +
  geom_smooth(method='lm')
```

### Problem

Get problem random effects:
```{r}
problem_eff = ranef(student_reg) %>%
  .$problem %>%
  rename('random_intercept' = '(Intercept)') %>%
  mutate(problem = as.numeric(rownames(.)),
         se = se.ranef(student_reg)$problem)
```

Plot random effects:
```{r}
ggplot(problem_eff, aes(x = reorder(problem, -random_intercept), y = random_intercept)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin=random_intercept-se, ymax=random_intercept+se), width=0) +
  theme_few(base_size=18) +
  xlab('Problems (reordered)') +
  ylab('Random intercepts') +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())

# ggsave('plots/problem_ranef.pdf', width=6.73, height=6.73/2)
```

```{r}
# Extract 24 hardest problems 

problems_ordered <- problem_eff %>% filter(random_intercept < 0) %>% dplyr::select(-se)

problems_ordered
```
```{r}
library(jsonlite)
json_data <- toJSON(problems_ordered, pretty = TRUE, auto_unbox = TRUE)

write(json_data, file = "hard_problems.json")

# hard problem indices
json_data <- toJSON(problems_ordered$problem, pretty = TRUE)

# Write the JSON array to a file
write(json_data, file = "hard_problems_indices.json")

```

```{r}
performance_by_problem = student_df %>%
  group_by(student, teacher, problem) %>%
  summarise(bonus = sum(bonus)) %>%
  group_by(problem) %>%
  summarise(avg_bonus = mean(bonus),
            sd_bonus = sd(bonus)) %>%
  left_join(problem_eff) %>%
  arrange(-random_intercept)

head(performance_by_problem)
tail(performance_by_problem)
```

Check: Are random intercepts correlated with average performance (as indexed by the amount of bonus awarded)?
```{r}
ggplot(performance_by_problem, aes(x=avg_bonus, y=random_intercept)) +
  geom_point() +
  geom_smooth(method='lm')
```